canaper: Categorical analysis of neo- and paleo-endemism in R

### 2022-09-06 ms/ms.Qmd
Add Box with definitions

**Box 1**: Columns in dataframe produced by `cpr_rand_test()`.

`cpr_rand_test()` calculates four basic metrics: `pd`, phylogenetic diversity (PD) [@Faith1992]; `rpd` [@Mishler2014], relative PD; `pe` [@Rosauer2009], phylogenetic endemism (PE); `rpe` relative PE [@Mishler2014].

>>>>

**Box 1**: Glossary of terms and metrics involved in categorical analysis of neo- and paleo-endemism (CANAPE)

- Community: A co-occurring set of species.
- Grid cell: One of a set of spatial units each with equal area that together cover a region of interest; each grid cell comprises a community.
- Community matrix: A 2-dimensional dataset with communties (grid cells) on one axis and species on the other.
- Phylogenetic diversity (PD): The total branch length (including the root) of a phylogenetic tree that includes all species occurring in a given area (community or grid cell) [@Faith1992].
- Phylogenetic endemism (PE): PD inversely weighted by the distribution range (i.e., number of grid cells) of a branch [@Rosauer2009].
- Relative phylogenetic diversity (RPD): The ratio of PD measured on the original tree vs. PD measured on a comparison tree where all branch lengths have been transformed to equal length [@Mishler2014].
- Relative phylogenetic endemism (RPE): The ratio of PE measured on the original tree vs. PE measured on a comparison tree where all branch lengths have been transformed to equal length [@Mishler2014].
- Neoendemic: An area with a high concentration of short, range-restricted branchlengths; may be due to processes such as recent speciation (radiation)
- Paleoendemic: An area with a high concentration of long, range-restricted branchlengths; may be due to processes such as extinction or colonization by distantly related species
- Mixed endemism: An area with a mixture of short and long, range-restricted branchlengths; may be due to multiple processes
- Super endemism: An area with mixed endemism that is statistically highly significant

**Box 2**: Columns in dataframe produced by `cpr_rand_test()`.

`cpr_rand_test()` calculates four basic metrics: `pd`, phylogenetic diversity (PD); `rpd` [@Mishler2014], relative PD; `pe` [@Rosauer2009], phylogenetic endemism (PE); `rpe` relative PE [@Mishler2014] (see Box 1 for an explanation of each).
